---
title: "Livelihoods in La Mixteca Alta"
author: "Carlos Dobler"
date: "March, 2021"
output: html_document
editor_options: 
  chunk_output_type: console
---


```{r setup, include=FALSE}

knitr::opts_chunk$set(
	fig.align = "center",
	message = FALSE,
	warning = FALSE,
	echo = FALSE)

```



```{r prep, include=FALSE}

# Load libraries
library(tidyverse)
library(corrr)
library(patchwork)
library(cluster)
library(randomForest)


# Prepare dataset
read_rds("out/df_livelihoods.RDS") %>%
  filter(total_income > 0) %>% # remove households with no reported activity
  
  mutate(
    
    # dichotomous
    across(c(maiz_irrigated_area,
             frijol_area,
             off_farm_ag_income),
           ~ifelse(.x > 0, "yes", "no") %>% factor(),
           .names = "{.col}_dich"),
    
    # bin migration (ordinal)
    migr_all_bin = cut(migr_all,
                       breaks = c(-Inf, 0, median(migr_all[migr_all > 0]), Inf),
                       labels = c("0", 
                                  median(migr_all[migr_all > 0]), # 1 
                                  str_c("> ", median(migr_all[migr_all > 0]))),
                       ordered_result = T)
    
    
  ) %>% 
  
  arrange(no_encuesta) -> df_livelihoods

```



```{r vars selection, include=FALSE}

vars_cluster <- c("maiz_rainfed_area",
                  "maiz_irrigated_area_dich",
                  "frijol_area_dich",
                  "livestock_value_sc",
                  "off_farm_ag_income_dich",
                  "sec_income_prop",
                  "terc_income_prop",
                  "migr_all_bin")

vars_predictors <- c("access_level",  
                     "marg",
                     # "pov_perc", #"pob_loc",
                     "land_hold", 
                     "riego", "tractor", "yunta", 
                     "vehicle", #"rooms", 
                     "procampo_dich", "prospera_dich",
                     "hh_size", 
                     "hh_adult_may",
                     "hh_male_adult", "hh_female_adult",
                     "hh_teenager", 
                     "hh_children", 
                     "sch_9", # "sch_ov9", # "sch_6", 
                     "total_income_sc")


```


```{r table, ignore = T}

# Descriptive statistics

# ds_a <- vector("list", 9)
# 
# tibble(v = "activities",
#        freq = "-",
#        mean = "-",
#        sd = "-") -> ds_a[[1]]
# 
# # agricultural
# df_livelihoods %>% 
#   select(maiz_rainfed_area,
#          maiz_irrigated_area_dich,
#          frijol_area_dich,
#          livestock_value_sc,
#          off_farm_ag_income_dich
#          ) %>% 
#   mutate(across(where(is.factor), ~case_when(.x == "yes" ~ 1L,
#                                              TRUE ~ NA_integer_)),
#          across(where(is.numeric), ~case_when(.x > 0 ~ 1L,
#                                              TRUE ~ NA_integer_))
#   ) %>% 
#   rowwise() %>% 
#   summarize(freq = ifelse(sum(c_across(everything()), na.rm = T) > 0, 1, 0)) %>%
#   summarize(v = "agricultural",
#             freq = as.character(round(sum(freq)/n() * 100)),
#             mean = "-",
#             sd = "-") -> ds_a[[2]]
# 
# # on-farm
# df_livelihoods %>% 
#   select(maiz_rainfed_area,
#          maiz_irrigated_area_dich,
#          frijol_area_dich,
#          livestock_value_sc
#          ) %>% 
#   mutate(across(where(is.factor), ~case_when(.x == "yes" ~ 1L,
#                                              TRUE ~ NA_integer_)),
#          across(where(is.numeric), ~case_when(.x > 0 ~ 1L,
#                                              TRUE ~ NA_integer_))
#   ) %>% 
#   rowwise() %>% 
#   summarize(freq = ifelse(sum(c_across(everything()), na.rm = T) > 0, 1, 0)) %>% 
#   summarize(v = "on-farm",
#             freq = as.character(round(sum(freq)/n() * 100)),
#             mean = "-",
#             sd = "-") -> ds_a[[3]]
# 
# # agricultural (dissaggregate)
# df_livelihoods %>% 
#   select(maiz_rainfed_area,
#          maiz_irrigated_area_dich,
#          frijol_area_dich,
#          livestock_value_sc,
#          off_farm_ag_income_dich
#   ) %>%
#   summarize(
#     across(everything(), 
#            list(
#              freq = ~ ifelse(is.factor(.x), 
#                              as.character(round(sum(.x == "yes")/n() * 100)), 
#                              as.character(round(sum(.x > 0)/n() * 100))),
#              mean = ~ ifelse(is.factor(.x), "-", as.character(round(mean(.x), 2))),
#              sd = ~ ifelse(is.factor(.x), "-", as.character(round(sd(.x), 2)))
#            )
#     )
#   ) %>% 
#   pivot_longer(everything(),
#                names_to = c("v", ".value"),
#                names_pattern = "(.+)_(.+)") -> ds_a[[4]]
#  
# # non-agricultural
# df_livelihoods %>% 
#   select("sec_income_prop",
#          "terc_income_prop",
#          "migr_all"
#          ) %>% 
#   mutate(across(where(is.numeric), ~case_when(.x > 0 ~ 1L,
#                                              TRUE ~ NA_integer_))
#   ) %>% 
#   rowwise() %>% 
#   summarize(freq = ifelse(sum(c_across(everything()), na.rm = T) > 0, 1, 0)) %>% 
#   summarize(v = "non-agricultural",
#             freq = as.character(round(sum(freq)/n() * 100)),
#             mean = "-",
#             sd = "-") -> ds_a[[5]]
# 
# # non-agricultural (sec and terc)
# df_livelihoods %>% 
#   select("sec_income_prop",
#          "terc_income_prop"
#   ) %>% 
#   summarize(
#     across(everything(), 
#            list(
#              freq = ~ as.character(round(sum(.x > 0)/n() * 100)),
#              mean = ~ as.character(round(mean(.x), 2)),
#              sd = ~ as.character(round(sd(.x), 2))
#            )
#     )
#   ) %>% 
#   pivot_longer(everything(),
#                names_to = c("v", ".value"),
#                names_pattern = "(.+)_(.+)") -> ds_a[[6]]
# 
# # non-agricultural (migr)
# df_livelihoods %>% 
#   summarize(
#     v = "migration",
#     freq = as.character(round(sum(migr_all > 0)/n() * 100)),
#     mean = "-",
#     sd = "-") -> ds_a[[7]]
# 
# # assets
# tibble(v = "assets",
#        freq = "-",
#        mean = "-",
#        sd = "-") -> ds_a[[8]]
# 
# df_livelihoods %>% 
#   select("land_hold", 
#          "riego", "tractor", "yunta", 
#          "vehicle", 
#          "procampo_dich", "prospera_dich",
#          "hh_size", 
#          "hh_adult_may",
#          "hh_male_adult", "hh_female_adult",
#          "hh_teenager", 
#          "hh_children", 
#          "sch_9", 
#          "total_income_sc"
#   ) %>%
#   summarize(
#     across(everything(), 
#            list(
#              freq = ~ ifelse(is.factor(.x), 
#                              as.character(round(sum(.x == "yes")/n() * 100)), 
#                              as.character(round(sum(.x > 0)/n() * 100))),
#              mean = ~ ifelse(is.factor(.x), "-", as.character(round(mean(.x), 2))),
#              sd = ~ ifelse(is.factor(.x), "-", as.character(round(sd(.x), 2)))
#            )
#     )
#   ) %>% 
#   pivot_longer(everything(),
#                names_to = c("v", ".value"),
#                names_pattern = "(.+)_(.+)") -> ds_a[[9]]
# 
# 
# bind_rows(ds_a) %>% 
#   write_csv("text/descriptive_stats.csv")



```


## Livelihood strategies
The clustering procedure recognized three main livelihood strategies:
```{r clustering, fig.width = 8.5, fig.asp = 0.250, dpi = 150}

# IGNORE ********************************************************
# df_livelihoods %>%
#   select(all_of(vars_cluster)) %>%
#   daisy(metric = "gower"#,
#             #weights = w
#             ) -> gw_dist
# 
# cmdscale(gw_dist, eig = T, k = 3) -> gw_cmd

# pam 
# pam(gw_cmd$points, k = 3, diss = T) %>% 
#   .$clustering %>% 
#   {mutate(df_livelihoods, cluster = factor(.))} -> df_livelihoods

# kmeans
# set.seed(123)
# kmeans(gw_cmd$points, centers = 3, nstart = 50) %>%
#   .$cluster %>%
#   {mutate(df_livelihoods, cluster = factor(.))} -> df_livelihoods

# hclust
# hclust(dist(gw_cmd$points), method = "single") %>% 
#   cutree(3) %>% 
#   {mutate(df_livelihoods, cluster = factor(.))} -> df_livelihoods

# *******************************************************************

# Clustering
df_livelihoods %>%
  select(all_of(vars_cluster)) %>%
  daisy(metric = "gower"#,
            # weights = c(3, 1, 1, 1, 1, 1, 1, 1)
            ) %>%

  pam(k = 3, diss = T) %>%
  .$clustering %>%

  {mutate(df_livelihoods, cluster = .)} %>% 
  mutate(cluster = case_when(cluster == 1 ~ 1,
                             cluster == 3 ~ 2,
                             cluster == 2 ~ 3) %>% factor()) -> df_livelihoods




# Function to obtain individual plots (per activity)
func_plot <- function(variable, pos = NA){
  
  df_livelihoods %>% 
    rename(vari = variable) -> df
  
  
  # Difference analysis among clusters
  
  # is variable continuous or ordinal?
  if(is.numeric(df$vari) | is.ordered(df$vari)){
    
    # omnibus test
    df %>% 
      {kruskal.test(vari ~ cluster, data = .)} %>% 
      .$p.value %>% 
      {ifelse(. < 0.001, "p < 0.001\n(K-W)", str_c("p = ", round(., 3), "\n(K-W)"))} -> omni_p
    
    # pairwise comparisons
    df %>%
      {pairwise.wilcox.test(as.numeric(.$vari), .$cluster, p.adjust.method = "holm")$p.value} %>%
      as_tibble(rownames = "V2") %>%
      pivot_longer(-1, names_to = "V1", values_to = "p") %>%
      filter(!is.na(p)) %>%
      mutate(v = str_c(V1, "-", V2)) -> pw
    
    
  # is variable categorical?
  } else {
    
    # omnibus test
    df %>%
      {chisq.test(.$vari, .$cluster, simulate.p.value = T)} %>%
      .$p.value %>%
      {ifelse(. < 0.001, "p < 0.001\n(Chi-sq.)", str_c("p = ", round(., 3), "\n(Chi-sq.)"))} -> omni_p

    # pairwise comparisons
    combn(seq_len(length(levels(df$cluster))), 2) %>%
      t() %>%
      as_tibble() %>%
      mutate(p = pmap_dbl(list(V1, V2), function(x, y){
        
        df %>%
          filter(cluster %in% c(x, y)) %>%
          {table(.$vari, as.numeric(.$cluster))} %>%
          {chisq.test(., simulate.p.value = T)} %>%
          .$p.value

      })) %>%

      mutate(p = ifelse(is.nan(p), 1, p.adjust(p, "holm"))) %>%
      mutate(v = str_c(V1, "-", V2)) -> pw
    
  }
  
  # assign letters of difference
  pw %>% pull(p) -> let
  names(let) <- pw %>% pull(v)
  
  tibble(cluster = levels(df$cluster)) %>%
    mutate(grp = multcompView::multcompLetters(let,
                                               compare = "<",
                                               threshold = 0.1,
                                               Letters = letters)$Letters) -> df_let
  
  
  # Generate plots
  
  # is variable continuous?
  if(is.numeric(df$vari)){

    df %>%
      group_by(cluster) %>%
      summarize(m = boxplot.stats(vari)$stats,
                a = mean(vari)) %>%
      ungroup() %>%
      mutate(stat = rep(str_c("y_",1:5), length(levels(df$cluster)))) %>%
      pivot_wider(names_from = stat, values_from = m) %>%
      left_join(df_let, by = "cluster") %>%

      ggplot(aes(x = cluster, fill = cluster)) +
      geom_boxplot(aes(ymin = y_1,
                       lower = y_2,
                       middle = y_2,
                       upper = y_4,
                       ymax = y_5),
                   stat = "identity", width = 0.7, fatten = NULL) +
      geom_point(aes(y = a)) +
      geom_text(aes(y = (max(y_5) - min(y_1))/15 + y_4, label = grp), nudge_x = 0.3, hjust = 0) +
      coord_flip() +
      scale_x_discrete(limits = rev(levels(df$cluster))) +
      scale_y_continuous(breaks = scales::breaks_extended(n = 3),
                         expand = expansion(mult = c(0.05, 0.15))) +
      theme(legend.position = "none") +
      labs(caption = omni_p,
           x = "strategy",
           y = variable %>% 
             str_remove_all('_bin|_dich|_area|_all|_sc') %>% 
             str_replace_all("_", " ") %>% 
             str_replace_all("income", "inc")
             ) -> p

    
  # is variable categorical or ordinal?
  } else {
    
    df %>%
      count(cluster, vari, .drop = F) %>% 
      group_by(cluster) %>% 
      mutate(m = round(n/sum(n)*100)) %>% 
      left_join(df_let, by = "cluster") %>% 
      
      group_by(cluster) %>% 
      mutate(v = row_number(),
             grp = ifelse(v == max(v), grp, NA)) %>% # keep only right-most letter
      ungroup() %>% 
      
      ggplot(aes(x = vari, y = cluster, fill = cluster)) +
      geom_tile(aes(alpha = m)) + # transparency
      geom_text(aes(label = m), nudge_x = -0.2, nudge_y = -0.2) +
      theme(legend.position = "none") +
      scale_y_discrete(limits = rev(levels(df$cluster))) +
      geom_text(aes(label = grp), nudge_x = 0.3, nudge_y = 0.3) +
      labs(caption = omni_p,
           y = "strategy",
           x = variable %>% 
             str_remove_all('_bin|_dich|_area|_income|_all|_sc') %>% 
             str_replace_all("_", " ")) -> p
  }
  
  
  # Assemble tibble (column with plots + a column to determine relative width)
  
  # remove axis if variable is not the first (left-most)
  if(is.na(pos)){
    
    p + theme(axis.text.y = element_blank(),
              axis.title.y = element_blank(),
              axis.ticks.y = element_blank()) -> p
    
  }
  
  p + theme(axis.title.x = element_text(size = 8)) -> p
  
  tibble(
    variable = variable,
    
    plot = list(p),
    
    var_width = ifelse(is.numeric(df$vari),
                       2,
                       length(levels(df$vari))) # wider widths for factor vars
  )
}




# Plot activities
vars_cluster[-1] %>%
  map_df(~func_plot(.x)) -> df_plot_activities
  
vars_cluster[1] %>% 
  map_df(~func_plot(vari = .x, pos = "x")) %>% 
  bind_rows(df_plot_activities) -> df_plot_activities

tibble(variable = vars_cluster) %>% # re-arrage based on order of given variables
  left_join(df_plot_activities, by = "variable") -> df_plot_activities

wrap_plots(df_plot_activities$plot,
           design = rep(seq_along(df_plot_activities$var_width), 
                        times = df_plot_activities$var_width) %>% 
             {LETTERS[.]} %>% 
             str_flatten())

```

## Random forest model
The random forest model predicts (classifies) livelihood strategies based on household assets and community characteristics (i.e., accessibility, poverty levels).

### Out-of-bag confusion matrix
(rows = observed, cols = predicted)  
```{r random forest err matrix}

# Fit random forest model
df_livelihoods %>% 
  select(cluster,
         all_of(vars_predictors)) -> df_classif
  
set.seed(123)
randomForest(cluster ~ ., data = df_classif, ntree = 1000, importance = T) -> rf
rm(df_classif)

rf$err.rate %>% .[nrow(.),1] %>% as.vector() -> oob_error
rf$confusion

```
Model's out-of-bag error rate: **`r round(oob_error*100, 2)`%**  

### Variables' importance
What variables best predict engagement with (membership to) the different livelihood strategies?
```{r importance, fig.width = 3.4, fig.asp = 1.2, out.width = '40%', dpi=150}

importance(rf, type = 1, scale = T) %>% 
  as_tibble(rownames = "var") %>%
  mutate(var = fct_reorder(var, MeanDecreaseAccuracy)) -> df_imp
  
df_imp %>% 
    ggplot(aes(y = MeanDecreaseAccuracy, x = var)) +
    geom_point(size = 2) +
    geom_segment(aes(x = var, xend = var, y = 0, yend = MeanDecreaseAccuracy)) +
    coord_flip() +
    labs(y = "Mean decrease accuracy") +
  theme(axis.title.y = element_blank())

```


### Partial dependency plots (modeled)
Modeled relationships (probabilities of membership) between livelihood strategies and predictors 
```{r pdp, fig.width = 7.6, fig.asp = 0.7, out.width = '90%', dpi=150}
func_pdp <- function(variable, pos = NA){
  
  rf$votes %>% 
    as.data.frame() %>% 
    as_tibble() %>% 
    bind_cols(df_livelihoods) %>% 
    select(1:3, variable) %>% 
    rename(vari = variable) %>% 
    
    mutate(vari = as.numeric(vari)) %>%
    
    pivot_longer(-vari, names_to = "cluster", values_to = "prob") -> df_votes
  
  # loop through clusters
  1:3 %>% 
    map(function(c){
      
      df_votes %>% 
        filter(cluster == c) %>% 
        loess(prob ~ vari, ., span = 1) -> l
        
      tibble(prob = predict(l, seq(min(df_votes$vari),
                                   max(df_votes$vari),
                                   length.out = 80)))
      
    }) %>% 
    bind_cols() %>%
    
    # standardize 
    rowwise() %>% 
    mutate(s = sum(c_across(1:3))) %>% 
    ungroup() %>% 
    mutate(across(1:3, ~.x/s)) %>% 
    select(-s) %>%
    
    mutate(x = seq(min(as.numeric(df_livelihoods[[variable]])),
                   max(as.numeric(df_livelihoods[[variable]])),
                   length.out = 80)) %>%
    
    pivot_longer(-x, names_to = "cluster", values_to = "prob") %>% 
    mutate(cluster = str_sub(cluster, -1) %>% factor()) %>% 
    
    # plot
    ggplot(aes(x = x, y = prob, fill = cluster)) +
    geom_area(color = "white") +
    labs(x = variable %>% 
           str_remove_all('_bin|_dich|_area|_all|_sc') %>% 
           str_replace_all("_", " ")) -> p
  
  # is variable continous?
  if(is.numeric(df_livelihoods[[variable]])){
    
    p + scale_x_continuous(breaks = scales::breaks_extended(n = 3)) -> p
    
  # is variable categorical or ordinal?
  } else {
    
    if(length(levels(df_livelihoods[[variable]])) == 2){
      h <- c(0,1)
    } else if (length(levels(df_livelihoods[[variable]])) == 3){
      h <- c(0,0.5,1)
    }
    
    p + scale_x_continuous(n.breaks = length(levels(df_livelihoods[[variable]])), 
                           labels = levels(df_livelihoods[[variable]])) +
      theme(axis.text.x = element_text(hjust = h)) -> p
    
  }
  
  # remove y axis text if variable is not the first (left-most)
  if(is.na(pos)){
    
    p + theme(axis.text.y = element_blank(),
              axis.title.y = element_blank(),
              axis.ticks.y = element_blank()) -> p
    
  }
  
  p + 
    theme(axis.title.x = element_text(size = 8)) +
    scale_y_continuous(breaks = scales::breaks_extended(n = 3)) -> p
  
  tibble(
    variable = variable,
    
    plot = list(p))
}



# Plot
df_imp %>% 
  {rev(levels(.$var))[-c(1, 7, 13)]} %>% 
  map_df(~func_pdp(vari = .x)) -> df_pdp

df_imp %>% 
  {rev(levels(.$var))[c(1, 7, 13)]} %>% 
  map_df(~func_pdp(vari = .x, pos = "x")) %>% 
  bind_rows(df_pdp) -> df_pdp

tibble(variable = rev(levels(df_imp$var))) %>% # re-arrage based on order of given variables
  left_join(df_pdp, by = "variable") -> df_pdp

# design
c(
  rep(1:6, each = 2) %>% 
             {LETTERS[.]} %>% 
             str_flatten(),
  
  "\n",
  
  rep(7:12, each = 2) %>% 
             {LETTERS[.]} %>% 
             str_flatten(),
  
  "\n",
  
  rep(13:nrow(df_pdp), each = 2) %>% 
             {LETTERS[.]} %>%
             c("##") %>% 
             str_flatten()
  
) %>% 
  str_flatten() -> des


wrap_plots(df_pdp$plot,
           design = des,
           guides = 'collect') & theme(legend.position = "bottom")

```

### Partial dependency plots (observed)
Observed relationships (relative frequency) between livelihood strategies and predictors
```{r pdp orig, fig.width = 7.6, fig.asp = 0.7, out.width = '90%', dpi=150}

func_pdp_obs <- function(variable, pos = NA){
  
  df_livelihoods %>% 
    select(cluster, variable) %>% 
    rename(vari = variable) -> df_votes
    
  if(is.factor(df_votes$vari) & !is.ordered(df_votes$vari)){
    
    df_votes %>% 
      count(cluster, vari, .drop = F) %>% 
      group_by(vari) %>% 
      mutate(rel_freq = n/sum(n),
             vari = as.numeric(vari)) %>% 
      ungroup() %>% 
      
      ggplot(aes(x = vari, y = rel_freq, fill = cluster)) +
      geom_area(color = "white") +
      labs(y = "rel. freq.",
           x = variable %>% 
             str_remove_all('_bin|_dich|_area|_all|_sc') %>% 
             str_replace_all("_", " ")) -> p
    
  } else {
    
    df_votes %>% 
      mutate(vari = as.numeric(vari)) -> df_votes
    
    # loop through clusters
    1:3 %>% 
      map_df(function(c){
        
        df_votes %>% 
          filter(cluster == c) %>% 
          pull(vari) %>% 
          density(n = 80, 
                  from = min(df_votes$vari),
                  to = max(df_votes$vari),
                  adjust = 3) -> l
        
        tibble(prob = l$y,
               x = l$x,
               # x = seq(min(as.numeric(df_livelihoods[[variable]])),
               #         max(as.numeric(df_livelihoods[[variable]])),
               #         length.out = 80),
               cluster = factor(c))
        
      }) %>%
      
      # standardize
      group_by(x) %>% 
      mutate(prob = prob/sum(prob)) %>% 
      ungroup() %>% 
      
      # plot
      ggplot(aes(x = x, y = prob, fill = cluster)) +
      geom_area(color = "white") +
      labs(y = "rel. freq.",
           x = variable %>% 
             str_remove_all('_bin|_dich|_area|_all|_sc') %>% 
             str_replace_all("_", " ")) -> p
    
  }
  
  # is variable continous?
  if(is.numeric(df_livelihoods[[variable]])){
    
    p + scale_x_continuous(breaks = scales::breaks_extended(n = 3)) -> p
    
  # is variable categorical or ordinal?
  } else {
    
    if(length(levels(df_livelihoods[[variable]])) == 2){
      h <- c(0,1)
    } else if (length(levels(df_livelihoods[[variable]])) == 3){
      h <- c(0,0.5,1)
    }
    
    p + 
      scale_x_continuous(n.breaks = length(levels(df_livelihoods[[variable]])), 
                         labels = levels(df_livelihoods[[variable]])) +
      theme(axis.text.x = element_text(hjust = h)) -> p
    
  }
  
  # remove y axis text if variable is not the first (left-most)
  if(is.na(pos)){
    
    p + theme(axis.text.y = element_blank(),
              axis.title.y = element_blank(),
              axis.ticks.y = element_blank()) -> p
    
  }
  
  p + 
    theme(axis.title.x = element_text(size = 8)) +
    scale_y_continuous(breaks = scales::breaks_extended(n = 3)) -> p
  
  tibble(
    variable = variable,
    
    plot = list(p))
}


# Plot
df_imp %>% 
  {rev(levels(.$var))[-c(1, 7, 13)]} %>% 
  map_df(~func_pdp_obs(vari = .x)) -> df_pdp

df_imp %>% 
  {rev(levels(.$var))[c(1,7,13)]} %>% 
  map_df(~func_pdp_obs(vari = .x, pos = "x")) %>% 
  bind_rows(df_pdp) -> df_pdp

tibble(variable = rev(levels(df_imp$var))) %>% # re-arrage based on order of given variables
  left_join(df_pdp, by = "variable") -> df_pdp

wrap_plots(df_pdp$plot,
           design = des,
           guides = 'collect') & theme(legend.position = "bottom")

```


Observed distribution of predictors by livelihood strategies:
```{r obsdist, fig.width = 8.5, fig.asp = 0.475, dpi = 150}

# Plot predictors
df_imp %>% 
  {rev(levels(.$var))[-c(1, 9)]} %>% 
  map_df(~func_plot(vari = .x)) -> df_obsdist

df_imp %>% 
  {rev(levels(.$var))[c(1, 9)]} %>% 
  map_df(~func_plot(vari = .x, pos = "x")) %>% 
  bind_rows(df_obsdist) -> df_obsdist

tibble(variable = rev(levels(df_imp$var))) %>% # re-arrage based on order of given variables
  left_join(df_obsdist, by = "variable") -> df_obsdist

# TEMP ******************
wrap_plots(df_obsdist$plot[1:8], widths = df_obsdist$var_width[1:8]) -> p_1
wrap_plots(df_obsdist$plot[9:17], widths = df_obsdist$var_width[9:17]) -> p_2

p_1/p_2


# ***********************

# # design
# c(rep(seq_along(df_obsdist$var_width)[1:8], 
#       times = df_obsdist$var_width[1:8]) %>% 
#              {LETTERS[.]} %>% 
#              str_flatten(),
#   
#   "#",
#   
#   "\n",
#   
#   rep(seq_along(df_obsdist$var_width)[9:17], 
#       times = df_obsdist$var_width[9:17]) %>% 
#              {LETTERS[.]} %>% 
#              str_flatten()
#   
#   ) %>% 
#   str_flatten() -> des
# 
# wrap_plots(df_obsdist$plot,
#            design = des)

```


Variables' definition:
```{r}

tribble(
  ~variable,                     ~definition,                           ~unit,
  "maiz_rainfed_area",           "area de maiz de temporal sembrado",   "ha",
  "maiz_irrigated_area_dich",    "siembra de maiz de riego",            "binario",
  "frijol_area_dich",            "siembra de frijol",                   "binario",
  "livestock_value_sc",          "valor total de ganado / 1000",        "pesos",
  "off_farm_ag_income_dich",     "empleo agrícola asalariado",          "binario",
  "sec_income_prop",             "porcentaje de miembros empleados en sector secundario","%",
  "terc_income_prop",            "porcentaje de miembros empleados en sector terciario", "%",
  "migr_all_bin",                "número de migrantes",                  "n",
  
  "access_level",                "nivel de accesibilidad nivel localidad (CONEVAL)", "NA (ordinal)", 
  "pov_perc",                    "porcentaje población en pobreza nivel municip. (CONEVAL)", "%",
  "land_hold",                   "posesión de tierras (superficie)",    "ha",
  "riego",                       "acceso a fuente de irrigación",       "binario",
  "tractor",                     "posesión de tractor",                 "binario",
  "yunta",                       "posesión de yunta",                   "binario",
  "vehicle",                     "posesión de vehículo",                "binario",
  "procampo_dich",               "participación en PROCAMPO",           "binario",
  "prospera_dich",               "participación en PROSPERA",           "binario",
  "hh_size",                     "número de miembros en el hogar",      "n",
  "hh_adult_may",                "porcentaje de miembros > 65 años",           "%",
  "hh_male_adult",               "porcentaje de hombres < 65 y > 18 años",     "%",
  "hh_female_adult",             "porcentaje de mujeres < 65 y > 18 años",     "%",
  "hh_teenager",                 "porcentaje de miembros < 18 y > 12 años",    "%",  
  "hh_children",                 "porcentaje de miembros < 12 años",           "%",
  "sch_9",                       "porcentaje de miembros con secundaria",      "%",
  "total_income_sc",             "ingreso total anual / 10000",         "pesos") %>% 
  
  mutate(variable = variable %>% 
           str_remove_all('_bin|_dich|_area|_all|_sc') %>% 
           str_replace_all("_", " ")) %>% 
  knitr::kable()

```

